### 2021-05-27 paper/terms/edge_set_def.tex

\isacommand{definition}\isamarkupfalse%
\ edge{\isacharunderscore}{\kern0pt}set\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharparenleft}{\kern0pt}{\isacharprime}{\kern0pt}v\ {\isasymtimes}\ {\isacharprime}{\kern0pt}v{\isacharparenright}{\kern0pt}\ set{\isachardoublequoteclose}\ \isakeyword{where}\isanewline
\ \ {\isachardoublequoteopen}edge{\isacharunderscore}{\kern0pt}set\ g\ {\isasymequiv}\ {\isacharbraceleft}{\kern0pt}{\isacharparenleft}{\kern0pt}u{\isacharcomma}{\kern0pt}v{\isacharparenright}{\kern0pt}\ {\isacharbar}{\kern0pt}\ u\ v{\isachardot}{\kern0pt}\ has{\isacharunderscore}{\kern0pt}edge\ g\ u\ v{\isacharbraceright}{\kern0pt}{\isachardoublequoteclose}\isanewline