### 2021-05-27 paper/terms/has_elem.tex

\isacommand{definition}\isamarkupfalse%
\ has{\isacharunderscore}{\kern0pt}vertex\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}v\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
\ \ {\isachardoublequoteopen}has{\isacharunderscore}{\kern0pt}vertex\ g\ u\ {\isasymequiv}\ vertex\ u\ {\isasymsqsubseteq}\ g{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{definition}\isamarkupfalse%
\ has{\isacharunderscore}{\kern0pt}edge\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}v\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}v\ {\isasymRightarrow}\ bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
\ \ {\isachardoublequoteopen}has{\isacharunderscore}{\kern0pt}edge\ g\ u\ v\ {\isasymequiv}\ edge\ u\ v\ {\isasymsqsubseteq}\ g{\isachardoublequoteclose}