### 2021-05-31 talk/terms/locale_primitives.tex
Finish slides

\isacommand{locale}\isamarkupfalse%
\ algebraic{\isacharunderscore}{\kern0pt}pre{\isacharunderscore}{\kern0pt}graph\ {\isacharequal}{\kern0pt}\ \isanewline
\ \ \isakeyword{fixes}\ empty\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isacharprime}{\kern0pt}g\ {\isacharparenleft}{\kern0pt}{\isachardoublequoteopen}{\isasymepsilon}{\isachardoublequoteclose}{\isacharparenright}{\kern0pt}\isanewline
\ \ \ \ \isakeyword{and}\ vertex\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}v\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g{\isachardoublequoteclose}\isanewline
\ \ \ \ \isakeyword{and}\ overlay\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isacartoucheopen}{+}{\isacartoucheclose}\ {\isadigit{7}}{\isadigit{5}}{\isacharparenright}{\kern0pt}\isanewline
\ \ \ \ \isakeyword{and}\ connect\ {\isacharcolon}{\kern0pt}{\isacharcolon}{\kern0pt}\ {\isachardoublequoteopen}{\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g\ {\isasymRightarrow}\ {\isacharprime}{\kern0pt}g{\isachardoublequoteclose}\ {\isacharparenleft}{\kern0pt}\isakeyword{infixl}\ {\isacartoucheopen}{\isasymrightarrow}{\isacartoucheclose}\ {\isadigit{8}}{\isadigit{0}}{\isacharparenright}{\kern0pt}